# Survey Analysis

### Scope  
`r length(all_data$scope)` participants estimated the number of new features completed until the next milstone. The following [boxplot](https://en.wikipedia.org/wiki/Box_plot) summarizes the results:  

```{r, fig.align='center', fig.height=2, fig.width=6, echo=FALSE, message=FALSE, warning=FALSE}
bwplot(all_data$scope, xlab='Scope (Number of Features)', 
       key=list(space="top", columns=3,
                text=list(lab=c("Median:","Average:", "Outcome:")),
                lines=list(
                        pch = c(16,4,NA),
                        col = c("black", "blue", "green"),
                        type = c("p", "p", "l"),
                        lwd = c(NA, NA, 3))),
       panel = function(x,y,...) {
        panel.bwplot(x,y,...)
        panel.points(x=mean(all_data$scope),y, pch=4, col="blue")
        panel.abline(v=actualScope, col="green", lwd=3)
})
```

**Properties for the [Diversity Prediction Theorem](https://www.youtube.com/watch?v=KtaaCAJjGr4):**  

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
n <- length(all_data$scope)
c <- mean(all_data$scope)  # crowd_prediciton
crowd_error <- (c - actualScope)^2
average_error <- 1/n * sum((all_data$scope - actualScope)^2)
diversity <- 1/n * sum((all_data$scope - c)^2)
Overall <- c(actualScope, 
             c,
             crowd_error,
             average_error,
             diversity)
dpt <- data.frame(Overall)
row.names(dpt) <- c('result', 'crowd prediction', 'crowd error', 'average error', 'diversity')
kable(dpt, digits = 2)
```

### Quality  
`r length(all_data$quality)` participants estimated the number of reported critical bugs in the first month. The following [boxplot](https://en.wikipedia.org/wiki/Box_plot) summarizes the results:  

```{r, fig.align='center', fig.height=2, fig.width=6, echo=FALSE, message=FALSE, warning=FALSE}
bwplot(all_data$quality, xlab='Quality (Number of reported critical bugs)', 
       key=list(space="top", columns=3,
                text=list(lab=c("Median:","Average:", "Outcome:")),
                lines=list(
                        pch = c(16,4,NA),
                        col = c("black", "blue", "green"),
                        type = c("p", "p", "l"),
                        lwd = c(NA, NA, 3))),
       panel = function(x,y,...) {
        panel.bwplot(x,y,...)
        panel.points(x=mean(all_data$quality),y, pch=4, col="blue")
        panel.abline(v=actualQuality, col="green", lwd=3)
})
```

**Properties for the [Diversity Prediction Theorem](https://www.youtube.com/watch?v=KtaaCAJjGr4):**  

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
n <- length(all_data$quality)
c <- mean(all_data$quality)  # crowd_prediciton
crowd_error <- (c - actualQuality)^2
average_error <- 1/n * sum((all_data$quality - actualQuality)^2)
diversity <- 1/n * sum((all_data$quality - c)^2)
Overall <- c(actualQuality, 
             c,
             crowd_error,
             average_error,
             diversity)
dpt <- data.frame(Overall)
row.names(dpt) <- c('result', 'crowd prediction', 'crowd error', 'average error', 'diversity')
kable(dpt, digits = 2)
```